### 2018-04-13 paper/overview.tex
finished pass on appendix

For example, consider $\cc{L}_9$. By the time \sys attempts to
synthesize an interpretation for $\cc{L}_9$ it will have solutions for
$\cc{L}_4$, $\cc{L}_6$, $\cc{L}_8$.
%
Possible interpretations of these predicates are shown in
\autoref{fig:ex-graph}.
%
The pre-formula is constructed from the bodies of clauses where
$\cc{L}_9$ is the head.
%
Each relational predicate, $P$,
is replaced by a corresponding boolean indicator variable, $\cc{b}_P$.
%
Each boolean indicator variable implies the solution for its
predicate,
encoded as the disjunction of the negation of the boolean
indicator variable and the solution.
%
In particular, the pre-formula for $\cc{L}_9$ is constructed from
clauses (5) and (6):
\begin{gather}
  ((\cc{b}_{\cc{L}_6} \land \cc{abs'} = \cc{n})
  \lor
  (\cc{b}_{\cc{L}_8} \land \cc{abs'} = -\cc{n}))
  \land
  (\neg \cc{b}_{\cc{L}_6} \lor \cc{n} \ge 0)
  \land
  (\neg \cc{b}_{\cc{L}_8} \lor \cc{n} < 0)
\end{gather}
%
The post-formula is constructed from clauses that transitively depend
on $\cc{L}_9$. Again, we replace relational predicates by
corresponding boolean indicators. However, we omit the boolean indicator for
$\cc{L}_9$. The post-formula is composed from clauses (1), (7), and
(8):
\begin{gather}
  (\neg \cc{b}_{\cc{dbl}} \lor \cc{d} = 2*\cc{x})
  \land
  (\neg \cc{b}_{\cc{main}} \lor
    (\cc{b}_{\cc{dbl}}
    \land \cc{abs'}= \cc{x}
    \land \cc{res}=\cc{d} ))
  \land
  (\cc{b}_{\cc{main}} \land \cc{res'} < 0)
\end{gather}
%
Interpolating the pre and post formulas yields an intepretation
of $\cc{L}_9$: $\cc{abs'} \geq 0$.
%
The procedure for solving a CDD system is described in formal detail
in \autoref{sec:solve-cdd}.

@@

%% talk about expansion:
\begin{figure}[t]
  \centering
  \begin{floatrow}[2]
    \ffigbox[.45\textwidth] {%
      {\caption{$\mcchc$ as a directed hypergraph. Each relational
          predicate is depicted as a graph node while each clause is
          represented by a hyperedge. Each hyperedge is labelled by the
          fact in the corresponding CHC\@. Each node has a valid
          corresponding interpretation, written in braces.
      }\label{fig:ex-graph}}}
      {\input{fig/example}}
    \ffigbox[.45\textwidth]
      {\caption{The hierarchy of classes of recursion-free CHC
          systems. Body Disjoint and Linear systems are subsumed by
          CDD systems. Solving Directly Solvable CHC systems is in
          co-NP while solving general, recursion-free systems is
          co-NEXPTIME Complete.
      }\label{fig:hierarchy}}
      {\input{fig/hierarchy}}
  \end{floatrow}
\end{figure}

>>>>

For example, consider $\cc{L}_9$. By the time \sys attempts to
synthesize an interpretation for $\cc{L}_9$ it will have solutions for
$\cc{L}_4$, $\cc{L}_6$, $\cc{L}_8$.
%
Possible interpretations of these predicates are shown in
\autoref{fig:ex-graph}.
%
The pre-formula is constructed from the bodies of clauses where
$\cc{L}_9$ is the head.
%
Each relational predicate, $P$,
is replaced by a corresponding boolean indicator variable, $\cc{b}_P$.
%
Each boolean indicator variable implies the solution for its
predicate,
encoded as the disjunction of the negation of the boolean
indicator variable and the solution.
%
In particular, the pre-formula for $\cc{L}_9$ is constructed from
clauses (5) and (6):
\begin{gather}
  ((\cc{b}_{\cc{L}_6} \land \cc{abs'} = \cc{n})
  \lor
  (\cc{b}_{\cc{L}_8} \land \cc{abs'} = -\cc{n}))
  \land
  (\neg \cc{b}_{\cc{L}_6} \lor \cc{n} \ge 0)
  \land
  (\neg \cc{b}_{\cc{L}_8} \lor \cc{n} < 0)
\end{gather}
%
The post-formula is constructed from clauses that transitively depend
on $\cc{L}_9$. Again, we replace relational predicates by
corresponding boolean indicators. However, we omit the boolean indicator for
$\cc{L}_9$. The post-formula is composed from clauses (1), (7), and
(8):
\begin{gather}
  (\neg \cc{b}_{\cc{dbl}} \lor \cc{d} = 2*\cc{x})
  \land
  (\neg \cc{b}_{\cc{main}} \lor
    (\cc{b}_{\cc{dbl}}
    \land \cc{abs'}= \cc{x}
    \land \cc{res}=\cc{d} ))
  \land
  (\cc{b}_{\cc{main}} \land \cc{res'} < 0)
\end{gather}
%
Interpolating the pre and post formulas yields an interpretation
of $\cc{L}_9$: $\cc{abs'} \geq 0$.
%
The procedure for solving a CDD system is described in formal detail
in \autoref{sec:solve-cdd}.

@@

%% talk about expansion:
\begin{figure}[t]
  \centering
  \begin{floatrow}[2]
    \ffigbox[.45\textwidth] {%
      {\caption{$\mcchc$ as a directed hypergraph. Each relational
          predicate is depicted as a graph node while each clause is
          represented by a hyperedge. Each hyperedge is labeled by the
          fact in the corresponding CHC\@. Each node has a valid
          corresponding interpretation, written in braces.
      }\label{fig:ex-graph}}}
      {\input{fig/example}}
    \ffigbox[.45\textwidth]
      {\caption{The hierarchy of classes of recursion-free CHC
          systems. Body Disjoint and Linear systems are subsumed by
          CDD systems. Solving Directly Solvable CHC systems is in
          co-NP while solving general, recursion-free systems is
          co-NEXPTIME Complete.
      }\label{fig:hierarchy}}
      {\input{fig/hierarchy}}
  \end{floatrow}
\end{figure}
